Interval Probability for Fuzzy Quantum Theories

### 2016-05-10 prob.tex
Add more Gerardo's comments and my respondce...

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\ffzd}[1]{{\mathbb{F}^{d\;*}_{#1}}}
\def\C{{\mathbb{C}}}
\newcommand{\ff}[1]{\mathbb{F}_{#1}}
\newcommand{\melement}[2]{ \langle #1 | #2 | #1 \rangle}
\newcommand{\expect}[2]{ \langle #1 | #2 | #1 \rangle}
\newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}

@@

>>>>

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\ffzd}[1]{{\mathbb{F}^{d\;*}_{#1}}}
\def\C{{\mathbb{C}}}
\newcommand{\ff}[1]{\mathbb{F}_{#1}}
\newcommand{\melement}[2]{ \langle #1 | #2 | #1 \rangle}
\newcommand{\expect}[2]{ \langle #1 | #2 | #1 \rangle}
\newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}
\newcommand{\gerardo}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{OliveGreen}{Gerardo says: #1}\end{minipage}}}
\newcommand{\andy}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{blue}{Andy says: #1}\end{minipage}}}

@@

\gerardo{Set-valued is a particular case?}

\yutsung{Set-valued is not a particular case of interval-valued probability.
In particular, the rule they respect are different. A real-valued
probability measure $\pmeas:\events\rightarrow[0,1]$ should satisfy
the following two rules:
\begin{enumerate}
\item $\pmeas(\Omega)=1$, and 
\item for a collection $E_{i}$ of pairwise disjoint events, $\pmeas(\bigcup_{i}E_{i})=\sum_{i}\pmeas(E_{i})$.
\end{enumerate}
When the range of $\pmeas$ is not only a real number, these conditions
cannot be both reserved. The set-valued probability measure preserves
Condition 2 and modifies Condition 1. The interval-valued probability
measure preserves Condition 1 and modifies Condition 2.

It seems hard to make a consistent story with the general set-valued
probability measure framework (except possible/impossible?), so we
just comment out set-valued probability measure here...}
